Classical density functional theory for the square-well liquid

### 2014-03-31 papers/square-well-liquid/paper.tex
added some thoughts to section IB of square well liquid paper Tested on elliot. Took 0:16.51.

@@

\fixme{We have an awesome theory.}

>>>>

\fixme{Some notes are as follows:}
In Gil-Villegas' paper, HS and Dispersion are wrapped up into the \textit{monomer} contribution, expressed in terms of energy densities as:
\[
  f_\text{mono} = f_\text{HS} - \frac{\alpha^\text{VDW}n}{kT}
\]
with $\alpha^\text{VDW}$ given by
\[
  \alpha^\text{VDW} = 2\pi\epsilon\int_\sigma^\infty r^2\phi(r)\,dr
\]
Then, the high-temp expansion is an expansion of the monomer term:
\[
  f_\text{mono} = f_\text{HS} + \beta a_1 + \beta^2 a_2 + \cdots
\]
\fixme{I'm not sure how to express this in terms of $F_\text{disp}[n]$ alone.}

@@

\fixme{We have an awesome theory. You should agree.}
